Reasoning About a Capability Machine with Local Capabilities

### 2017-09-29 esop-2018/paper.tex
Attempt to make the paragraph about readCond more readable.

For capabilities with read permission, the $\readCond{}$ ensures that it can
only be used to read safe words, i.e.\ words in the value relation.
This is done by imposing an upper bound on the memory requirements of the region
governing the addressed memory. The upper bound is formulated in terms of a
standard region $\iota^\pwl_{\start,\addrend}$, which requires all the words in
the range $[\start,\addrend]$ to be safe, i.e.\ in the value relation. The
region governing the addressed memory must be at least as restrictive as the
standard region. The read condition also takes into account the locality of the
capability because, generally speaking, global capabilities should only depend
on permanent regions. Concretely, we use the function
$\var{localityReg}(\gl,W)$, which projects out all active (non-revoked) regions
when the locality $\gl$ is local, but only the permanent regions when $\gl$ is
global. Note finally that the step-indexing described in
\sectionname~\ref{sec:formalizing-guarantees} is effectively at play here, but hidden
in the definition of the standard region $\iota^\pwl_{\start,\addrend}$, which
we omit for space reasons.

>>>>

For capabilities with read permission, the $\readCond{}$ ensures that it can
only be used to read safe words, i.e.\ words in the value relation. To guarantee
this, we require that the addressed memory is governed by a region $W(r)$ that
imposes safety as a requirement on the values contained. This safety requirement
is formulated in terms of a standard region $\iota^\pwl_{\start,\addrend}$. The
definition of that standard island is omitted for space reasons, but it simply
requires all the words in the range $[\start,\addrend]$ to be safe, i.e.\ in the
value relation. Requiring that $W(r)\nsubsim[n]\iota^\pwl_{\start,\addrend}$
means that $W(r)$ must accept only safe values like
$\iota^\pwl_{\start,\addrend}$, but can be even more restrictive if desired. The
read condition also takes into account the locality of the capability because,
generally speaking, global capabilities should only depend on permanent regions.
Concretely, we use the function $\var{localityReg}(\gl,W)$, which projects out
all active (non-revoked) regions when the locality $\gl$ is local, but only the
permanent regions when $\gl$ is global. Note finally that the step-indexing
described in \sectionname~\ref{sec:formalizing-guarantees} is effectively at
play here, but hidden in the definition of the standard region
$\iota^\pwl_{\start,\addrend}$, which we omit for space reasons.
